Really Good Title

### 2019-01-07 documentation/paper.tex
Some stuff for two-species all vs best

\begin{figure}[H]
\center
\begin{tabular}{ccc}
Standard & Per-individual s. a. & Per-parameter s. a. \\
\includegraphics[width=0.3\textwidth]{img/standard_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} \\
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:changing opponent}
\end{figure}

@@

This implementation of the idea from \cite{Sims94evolving3d} uses two species that are always evaluated against the other.

@@

\begin{figure}[H]
\center
\includegraphics[width=0.155555\textwidth]{img/scheme_self_training_2.png}
\caption{Scheme for self training variant 1}
\label{fig:scheme_self_training_2}
\end{figure}

\begin{figure}[H]
\center
\begin{tabular}{cc}
left side & right side \\
\includegraphics[width=0.3\textwidth]{img/standard_self_training_2_1.png} &
\includegraphics[width=0.3\textwidth]{img/standard_self_training_2_2.png} \\
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum standard mutation.}
\label{fig:standard_self_training_2}
\end{figure}

\todo{too much diversity}

\begin{figure}[H]
\center
\begin{tabular}{cc}
left side & right side \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_self_training_2_1_oldrun.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_self_training_2_2_oldrun.png}
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum with self adapt 1.}
\label{fig:self_adapt_1_self_training_2_oldrun}
\end{figure}

>>>>

\begin{figure}[H]
\center
\begin{tabular}{ccc}
standard & per-individual s. a. & per-parameter s. a. \\
\includegraphics[width=0.3\textwidth]{img/standard_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} \\
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:changing opponent}
\end{figure}

@@

This implementation of the idea from \cite{Sims94evolving3d} uses two species that are always evaluated against the other. We evaluated

@@

\begin{figure}[H]
\center
\includegraphics[width=0.155555\textwidth]{img/scheme_self_training_2.png}
\caption{Scheme for two-species all vs best self training; source: \cite{Sims94evolving3d}.}
\label{fig:scheme_self_training_2}
\end{figure}

\begin{figure}[H]
\center
\begin{tabular}{cc}
standard left side & standard right side \\
\includegraphics[width=0.3\textwidth]{img/standard_self_training_2_1.png} &
\includegraphics[width=0.3\textwidth]{img/standard_self_training_2_2.png} \\
self-adapt left side & self-adapt right side \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_self_training_2_1_oldrun.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_self_training_2_2_oldrun.png}
\end{tabular}
\caption{Fitness density two-species all vs best method with indicated minimum, average and maximum.}
\label{fig:self_adapt_1_self_training_2_oldrun}
\end{figure}

In this scenario \ref{fig:self_adapt_1_self_training_2_oldrun}
